### 2019-08-13 scache/tii/coverletter/coverletter.tex
mkdir scache

This paper is the extension of our conference paper at PPoPP '18 \cite{fu2018efficient}. 
In the manuscript we uploaded, we highlight the new content in blue.
This paper makes the following distinct contributions compared with the conference paper.

\begin{enumerate}
\item 
We propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model.
The FRQ model quantifies computing and I/O resources by five input parameters. 
Furthermore, the FRQ model visualizes the resources scheduling strategies of the DAG frameworks in the time dimension. 
In this paper, we use the model to analyze the deficiencies of the resources scheduling strategies and then optimize them.
\item 
In the conference paper, we only implement SCache on Spark. 
In this paper, we implement SCache on Hadoop MapReduce. 
By using the FRQ model to analyze Hadoop MapReduce, we can figure out that SCache is feasible to optimize the shuffle phases. 
Meanwhile, our experiments are also consistent with the analysis of the model.
This result demonstrates the compatibility and adaptability of SCache as a cross-framework plug-in.
% To demonstrate the compatibility and adaptability of SCache as a cross-framework plug-in, we also extended SCache on Hadoop MapReduce. 
\item
We append two parts to the evaluation section. 
Firstly, we evaluate the FRQ model in both our in-house environment and Amazon EC2 environment. The error between the FRQ’s calculated value and the experimental value is mainly below $10\%$. 
Secondly, we evaluate the performance of Hadoop MapReduce with SCache. We use the same Amazon EC2 environment as the conference paper (50-nodes m4.xlarge cluster).
According to the experiments, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$.
\end{enumerate}

% Besides the major contributions, we also revise the paper in many places, including writing and more related work. 
In summary, we propose a new performance model to provide a theoretical basis for performance optimization and improve experiments by adding experiments on Hadoop MapReduce. 
We believe that the added content makes a sufficient contribution to this journal submission.

\bibliographystyle{IEEEtran}
\bibliography{coverletter}

>>>>

% This paper is the extension of our conference paper at PPoPP '18 \cite{fu2018efficient}. 
This paper is the extension of our conference paper at PPoPP. 
% In the manuscript we uploaded, we highlight the new content in blue.
% We believe that shuffle-heavy jobs are also existed widely in industrial big-data analysis.
% SCache can also provide considerable optimization in industrial big-data.
In this paper, we combine the characteristic of the industrial big-data and DAG computing frameworks.
We provide a new data processing solution for the industrial big-data based on our conference paper.
Besides, we use the credible benchmark to demonstrate that our solution is effective in the industrial big-data analysis.
This paper makes the following distinct contributions compared with the conference paper.

\begin{enumerate}
\item 
We propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model.
The FRQ model quantifies computing and I/O resources by five input parameters. 
Furthermore, the FRQ model visualizes the resources scheduling strategies of the DAG frameworks in the time dimension. 
In this paper, we use the model to evaluate the deficiencies of different resources scheduling strategies and then optimize them.
\item 
In the conference paper, we only implement SCache on Spark. 
In this paper, we also implement SCache on Hadoop MapReduce, since Spark and Hadoop MapReduce are the two most distributed computing frameworks using in industrial big-data analysis.
% By using the FRQ model to analyze Hadoop MapReduce, we can figure out that SCache is feasible to optimize the shuffle phases. 
% Meanwhile, our experiments are also consistent with the analysis of the model.
This result also demonstrates the compatibility and adaptability of SCache as a cross-framework plug-in.
% To demonstrate the compatibility and adaptability of SCache as a cross-framework plug-in, we also extended SCache on Hadoop MapReduce. 
\item
We append two parts to the evaluation section. 
Firstly, we evaluate the FRQ model in both our in-house environment and Amazon EC2 environment. The error between the FRQ’s calculated value and the experimental value is mainly below $10\%$. 
Secondly, we evaluate the performance of Hadoop MapReduce with SCache. We use the same Amazon EC2 environment as the conference paper (50-nodes m4.xlarge cluster).
According to the experiments, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$.
\end{enumerate}

% Besides the major contributions, we also revise the paper in many places, including writing and more related work. 
In summary, we propose a new performance model to provide a theoretical basis for performance optimization and improve evaluations by adding experiments on Hadoop MapReduce. 
We believe that the added content makes a sufficient contribution to this special issue.
% We believe that the added content makes a sufficient contribution to this journal submission.

\bibliographystyle{IEEEtran}
% \bibliography{coverletter}

### 2019-08-13 scache/tii/tex/conclusion.tex

\section{Conclusion}
In this paper, we present SCache, a cross-framework shuffle optimization for DAG computing frameworks. 
SCache decouples the shuffle from computing tasks and leverages memory to store shuffle data. 
By task pre-scheduling and shuffle data pre-fetching with application context, SCache significantly mitigates the shuffle overhead. 
%  {\color{red}
%  Our implementation with Spark and evaluations show that SCache can provide a promising speedup to the DAG framework. 
%  }
{\color{black}
% Our evaluations on Spark and Hadoop MapReduce with SCache show that SCache can provide a promising speedup. 
The benchmark using in evaluations covers the most situations of industrial big-data analysis.
The evaluations show that SCache can provide a promising speedup in both traditional and industrial big-data workloads. 
Furthermore, we propose \textit{Framework Resources Quantification} (FRQ) model to assist in analyzing shuffle process of DAG computing frameworks. At last, we evaluate the SCache shuffle optimization by the FRQ model.
% Therefore, with the shared defects of shuffle among different frameworks, we believe that the optimization of SCache is general and easy to be adapted. 
}

>>>>

\section{Conclusion}\label{conclusion}
In this paper, we present SCache, a cross-framework shuffle optimization for DAG computing frameworks. 
SCache decouples the shuffle from computing tasks and leverages memory to store shuffle data. 
By task pre-scheduling and shuffle data pre-fetching with application context, SCache significantly mitigates the shuffle overhead. 
%  {\color{red}
%  Our implementation with Spark and evaluations show that SCache can provide a promising speedup to the DAG framework. 
%  }
{\color{black}
% Our evaluations on Spark and Hadoop MapReduce with SCache show that SCache can provide a promising speedup. 
% The benchmark using in evaluations covers the most situations of industrial big-data analysis.
The evaluations show that SCache can provide a promising speedup in both traditional and industrial big-data workloads. 
Furthermore, we propose \textit{Framework Resources Quantification} (FRQ) model to assist in analyzing shuffle process of DAG computing frameworks. 
% At last, we evaluate the SCache shuffle optimization by the FRQ model.
% Therefore, with the shared defects of shuffle among different frameworks, we believe that the optimization of SCache is general and easy to be adapted. 
}

### 2019-08-13 scache/tii/tex/evaluation.tex

\section{Evaluation}\label{evaluation}
{\color{blue}
This section reveals the evaluation of SCache with comprehensive workloads and benchmarks which include common operations in the industrial big-data analysis. 
% To show the compatibility of SCache as a cross-framework plug-in, we implement and evaluate SCache on both Spark and Hadoop MapReduce. 
We implement and evaluate SCache on Spark and Hadoop MapReduce, since they are the two most distributed computing frameworks using in industrial big-data analysis.
First, we evaluate the Spark with SCache in 3 different benchmarks.
We run a Spark job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.
To prove the performance gain of SCache with a industrial production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
% In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
% To prove the compatibility of SCache as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
Second, due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
}
Finally, we measure the overhead of weighted reservoir sampling.

In summary, SCache can decrease ~$89\%$ time of Spark shuffle without introducing extra network transfer.
More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying the optimization from SCache.
{\color{blue}Meanwhile, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$}

% Because a complex Spark application consists of multiple stages. The completion time of each stage varies under different input data, configurations and different number of stages. This uncertainty leads to the dilemma that dramatic fluctuation occurs in overall performance comparison. To present a straightforward illustration, we limit the scope of most evaluations in a single stage.
\begin{figure*}
	\centering
	\begin{minipage}[t]{.32\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/groupbymapstage}
				\caption{Map Stage Completion Time}
				\label{fig:mapstage}
			\end{minipage}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/groupbyreducestage}
				\caption{Reduce Stage Completion Time\newline}
				\label{fig:reducestage}	
			\end{minipage}
		\end{subfigure}
		\vspace{-1em}
		\caption{Stage Completion Time of\newline Single Shuffle Test}
		\label{fig:singleshuffle}
	\end{minipage}	
	\begin{minipage}[t]{.32\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/groupbymaptask}
				\caption{Median Task in Map Stages}
				\label{fig:maptask}
			\end{minipage}

			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/groupbyreducetask}
				\caption{Median Task in Reduce Stages\newline}
				\label{fig:reducetask}
			\end{minipage}
		\end{subfigure}
		\vspace{-1em}
		\caption{Median Task Completion\newline Time of Single Shuffle Test}
		\label{fig:singleshuffletask}
	\end{minipage}	
	\begin{minipage}[t]{.32\linewidth}
		\begin{subfigure}{\linewidth}
			\vspace{-0.5em}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/tera}
				\caption{Reduce Stage of First Shuffle}
				\label{fig:terasort}
			\end{minipage}

			\begin{minipage}{\linewidth}
				\vspace{0.5em}
				\includegraphics[width=\linewidth]{fig/tera_shuffle}
				\caption{Network Traffic of Second Shuffle}
				\label{fig:terashuffle}
			\end{minipage}
		\end{subfigure}
		% \vspace{0.1em}
		\caption{Terasort Evaluation}
	\end{minipage}
\end{figure*}

\subsection{Setup}\label{stepup}
We modified Spark to enable shuffle optimization of SCache as a representative.
The shuffle configuration of Spark is set to the default\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}. 
We run the experiments on a 50-node m4.xlarge cluster on Amazon EC2\footnote{http://aws.amazon.com/ec2/}. 
Each node has 16GB memory and 4 CPUs. The network bandwidth provided by Amazon is insufficient. 
Our evaluations reveal the bandwidth is only about 300 Mbps (see Figure \ref{fig:util}).

@@

\subsubsection{Simple DAG Analysis}\label{simpledag}
%\subsubsection{Hardware Utilization}
We first run the same single shuffle test shown in Figure \ref{fig:util}. 
For each stage, we run 5 rounds of tasks with different input size. 
As shown in Figure \ref{fig:scache_util}, the hardware utilization is captured from one node during the job. 
Note that since the completion time of whole job is about $50\%$ less than Spark without SCache, the duration of Figure \ref{fig:scache_util} is cut in half as well. 
An overlap among CPU, disk, and network can be easily observed in Figure \ref{fig:scache_util}. 
It is because the decoupling of shuffle prevents the computing resource from being blocked by I/O operations. 
On the one hand, the decoupling of shuffle write helps free the slot earlier, so that it can be re-scheduled to a new map task.
On the other hand, with the help of shuffle pre-fetching, the decoupling of shuffle read significantly decreases the CPU idle time at the beginning of a reduce task.
At the same time, SCache manages the hardware resources to store and transfer shuffle data without interrupting the computing process.
As a result, the utilization and multiplexing of hardware resource are increased, thus improving the performance of Spark. 
The performance evaluation in Figure \ref{fig:singleshuffletask} shows the consistent results with our observation of hardware utilization. 
% By running Spark with SCache, the completion time of map stage can be reduced $10\%$ on average. 
% For reduce stage, instead, SCache achieves a ~$75\%$ performance gain in the completion time of the reduce stage.
% A detail analysis into the nutshell of varied overall performance gain on different stages is presented with Figure \ref{fig:singleshuffletask}. 
For each stage, we pick the task that has median completion time. 
In the map task, the disk operations are replaced by the memory copies to decouple the shuffle write. 
It helps eliminate $40\%$ of shuffle write time (Figure \ref{fig:maptask}), which leads to a $10\%$ improvement of map stage completion time in Figure \ref{fig:mapstage}. 
Note that the shuffle write time can be observed even with the optimization of SCache. 
The reason is that before moving data out of Spark's JVM, the serialization is inevitable and CPU intensive \cite{makingsense}.

In the reduce task, most of the shuffle overhead is introduced by network transfer delay. 
By doing shuffle data pre-fetching based on the pre-scheduling results, the explicit network transfer is perfectly overlapped in the map stage. 
With the help of the co-scheduling scheme, SCache guarantees that each reduce task has the benefit of shuffle pre-fetching. 
The in-memory cache of shuffle data further reduces the shuffle read time. 
As a result, the combination of these optimizations decreases ~$100\%$ overhead of the shuffle read in a reduce task (Figure \ref{fig:reducetask}). 
In addition, the heuristic algorithm can achieve a balanced pre-scheduling result, thus providing ~$80\%$ improvement in reduce stage completion time (Figure \ref{fig:reducestage}).

@@

\subsubsection{Terasort}
We also evaluate Terasort\cite{terasort} --- a recognized shuffle intensive benchmark for distributed system analysis. 
Terasort consists of two consecutive shuffles. 
The first shuffle reads the input data and uses a hash partition function for re-partitioning. 
As shown in Figure \ref{fig:terasort}, Spark with SCache runs 2 $\times$ faster during the reduce stage of the first shuffle, which is consistent with the results in Section \ref{simpledag}. 
It further proves the effectiveness of SCache's optimization.

The second shuffle of Terasort partitions the data through a Spark RangePartitioner. 
% As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task. So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.
In the second shuffle, almost $93\%$ of input data of a reduce task is produced by one particular map task. 
So we take the second shuffle as an extreme case to evaluate the heuristic locality swap of SCache.
In this shuffle, Spark schedules a reduce task to the node that produces most input data. 
By doing this, Spark minimizes the shuffle data through network. 
At the same time, Figure \ref{fig:terashuffle} reveals that SCache produces exactly same network traffic as Spark. 
It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load. 
\begin{figure*}
	\centering
	\includegraphics[width=.9\textwidth]{fig/tpcds}
	\caption{TPC-DS Benchmark Evaluation}
	\label{fig:tpcds}
	\vspace{-1em}
\end{figure*}

\subsubsection{Industrial Production Workload}
We also evaluate some queries from TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.). 
TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. 
% We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute. 
As shown in Figure \ref{fig:tpcds}, the horizontal axis is query name and the vertical axis is query completion time. 
Note that we skip some queries due to the compatible issues. 
Spark with SCache outperforms the original Spark in almost all tested queries. 
Furthermore, in many queries, Spark with SCache outperforms original Spark by an order of magnitude. 
It is because that those queries contain shuffle-heavy operations such as \textit{groupby}, \textit{union}, etc.
The overall reduction portion of query time that SCache achieved is $40\%$ on average. 
Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.

\begin{figure*}
	\centering
	\begin{subfigure}{.47\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_terasort_scache}
		\caption{\color{blue}Hadoop MapReduce with SCache}
		\label{fig:hadoop_terasort_scache}
	\end{subfigure}
	\begin{subfigure}{.47\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_terasort_origin}
		\caption{\color{blue}Hadoop MapReduce without SCache}
		\label{fig:hadoop_terasort_origin}
	\end{subfigure}
	\caption{\color{blue}CPU utilization and I/O throughput of a node during a Hadoop MapReduce Terasort job}
	\label{fig:hadoop_terasort}
\end{figure*}

{\color{blue}
\subsection{Hadoop MapReduce with SCache}

@@

% Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort. Both figures have the same proportion of time. 
As Figure \ref{fig:hadoop_terasort} shows, Hadoop MapReduce with SCache brings $15\%$ of total time optimization with 384GB input data size. 
As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase. The shuffle phase and the reduce phase start simultaneously. Because a large amount of shuffle data reaches the network bottleneck, the beginning part of reduce phase needs to wait for network transfer. This causes the CPU resources to be idle. 
On the other hand, in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache starts pre-fetching in the map phase. This avoids the reduce phase waiting for the shuffle data. Furthermore, pre-fetching utilizes the idle I/O throughput in the map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop MapReduce with SCache optimizes Terasort overall completion time by up to $15\%$ and an average of $13\%$ with input data sizes from 128GB to 512GB.
}

\subsection{Overhead of Sampling}
We evaluate the overhead of sampling with different input sizes and numbers of nodes. 
In Figure \ref{fig:sampling}, the overhead of sampling only grows with the increase of input size on each node, but remains relatively stable when the cluster size scales up.
Since the shuffle data is short-lived, write-once, and read-once, the central controller of SCache does not have to collect and manage complex metadata. 
Meanwhile, most of the optimizations such as fetching and storing shuffle data are finished by workers independently. 
So the cost of pre-scheduling algorithm and memory management are unlikely to make the master become the bottleneck of the scalability.
Combined with the sampling overhead evaluation, we believe that SCache is scalable.

\begin{figure}
    \centering
    \begin{minipage}{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{fig/hadoop_terasort_time} % first figure itself
        \caption{\color{blue}Hadoop MapReduce Terasort Completion Time}
		\label{fig:hadoop_terasort_time}
    \end{minipage}\hfill
    \begin{minipage}{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{fig/sampling} % second figure itself
        \caption{Sampling Overhead}
		\label{fig:sampling}
    \end{minipage}
\end{figure}

>>>>

\section{Evaluation}\label{evaluation}

This section reveals the evaluation of SCache with comprehensive workloads and benchmarks which include common operations in the industrial big-data analysis. 
% To show the compatibility of SCache as a cross-framework plug-in, we implement and evaluate SCache on both Spark and Hadoop MapReduce. 
We implement and evaluate SCache on Spark and Hadoop MapReduce, since they are the two most distributed computing frameworks using in industrial big-data analysis.
% First, we evaluate the Spark with SCache in two different benchmarks.
% We run a Spark job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
% Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.
% To prove the performance gain of SCache with a industrial production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
% In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
% To prove the compatibility of SCache as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
% Second, due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
% Finally, we measure the overhead of weighted reservoir sampling. 
In summary, SCache decrease ~$89\%$ time of Spark shuffle without introducing extra network transfer.
More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying the optimization from SCache.
{\color{black}Meanwhile, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$.}

% Because a complex Spark application consists of multiple stages. The completion time of each stage varies under different input data, configurations and different number of stages. This uncertainty leads to the dilemma that dramatic fluctuation occurs in overall performance comparison. To present a straightforward illustration, we limit the scope of most evaluations in a single stage.

\begin{figure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/util}
		\caption{Spark without SCache}
		\label{fig:util}
	\end{subfigure}
	% \vspace{-1em}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/scache_util}
		\caption{Spark with SCache}
		\label{fig:scache_util}
	\end{subfigure}
	\caption{CPU Utilization and I/O Throughput of a Node During a Spark Single Shuffle Application}
	\label{fig:simple_spark}
\end{figure}

\begin{figure*}
	\centering
	\begin{minipage}[t]{.5\textwidth}
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=\linewidth]{fig/groupbymapstage}
		\caption{Map Stage Completion Time}
		\label{fig:mapstage}
	\end{subfigure}
	\begin{subfigure}{.49\linewidth}
		\includegraphics[width=\linewidth]{fig/groupbyreducestage}
		\caption{Reduce Stage Completion Time}
		\label{fig:reducestage}	
	\end{subfigure}
	\caption{Stage Completion Time of Single Shuffle Test}
	\label{fig:singleshuffle}
	\end{minipage}	
	\begin{minipage}[t]{.49\textwidth}
		\begin{subfigure}{.5\linewidth}
			\includegraphics[width=\linewidth]{fig/groupbymaptask}
			\caption{Median Task in Map Stages}
			\label{fig:maptask}
		\end{subfigure}
		\begin{subfigure}{.49\linewidth}
			\includegraphics[width=\linewidth]{fig/groupbyreducetask}
			\caption{Median Task in Reduce Stages}
			\label{fig:reducetask}
		\end{subfigure}
		% \vspace{-1em}
		\caption{Median Task Completion Time of Single Shuffle Test}
		\label{fig:singleshuffletask}
	\end{minipage}	
\end{figure*}

\subsection{Setup}\label{stepup}
% We modified Spark to enable shuffle optimization of SCache as a representative.
The shuffle configuration of Spark is set to the default\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}. 
We run the experiments on a 50-node m4.xlarge cluster on Amazon EC2\footnote{http://aws.amazon.com/ec2/}. 
Each node has 16GB memory and 4 CPUs. The network bandwidth provided by Amazon is insufficient. 
Our evaluations reveal the bandwidth is only about 300 Mbps.
%  (see Figure \ref{fig:util}).

@@

\subsubsection{Simple DAG Analysis}\label{simpledag}
% As shown in Figure \ref{fig:scache_util}, we first run the same single shuffle test shown in Figure \ref{fig:util}. 
We first run Spark's \textit{GroupByTest} on Amazon EC2.
This job has 2 rounds of tasks for each node.
% We first run the same single shuffle test shown in Figure \ref{fig:util}. 
% For each stage, we run 5 rounds of tasks with different input size. 
As shown in Figure \ref{fig:simple_spark}, the hardware utilization is captured from one node during the job. 
Note that since the completion time of the job with SCache is about $50\%$ less than Spark without SCache, the duration of Figure \ref{fig:scache_util} is only half of Figure \ref{fig:util}.
As shown in \ref{fig:util}, the network transfer of shuffle data introduces an explicit I/O delay during \textit{shuffle read}.
And the several bursts of network traffic in \textit{shuffle read} result in network congestion.
As shown in Figure \ref{fig:scache_util}, an overlap among CPU, disk, and network can be easily observed. 
It is because the decoupling of shuffle prevents the computing resource from being blocked by I/O operations. 
On the one hand, the decoupling of shuffle write helps free the slot earlier, so that it can be re-scheduled to a new map task.
On the other hand, with the help of shuffle pre-fetching, the decoupling of shuffle read significantly decreases the CPU idle time at the beginning of a reduce task.
At the same time, SCache manages the hardware resources to store and transfer shuffle data without interrupting the computing process.
As a result, the utilization and multiplexing of hardware resource are increased, thus improving the performance of Spark.

% The performance evaluation in Figure \ref{fig:singleshuffletask} shows the consistent results with our observation of hardware utilization. 
% For each stage, we pick the task that has median completion time. 
In the map stage, the disk operations are replaced by the memory copies to decouple the shuffle write. 
It helps eliminate $40\%$ of shuffle write time (Figure \ref{fig:maptask}), which leads to a $10\%$ improvement of map stage completion time in Figure \ref{fig:mapstage}. 
% Note that the shuffle write time can be observed even with the optimization of SCache. 
% The reason is that before moving data out of Spark's JVM, the serialization is inevitable and CPU intensive \cite{makingsense}. 
In the reduce stage, most of the shuffle overhead is introduced by network transfer delay. 
By doing shuffle data pre-fetching, the explicit network transfer is perfectly overlapped in the map stage. 
% By doing shuffle data pre-fetching based on the pre-scheduling results, the explicit network transfer is perfectly overlapped in the map stage. 
% With the help of the co-scheduling scheme, SCache guarantees that each reduce task has the benefit of shuffle pre-fetching. 
% The in-memory cache of shuffle data further reduces the shuffle read time. 
As a result, the combination of these optimizations decreases ~$100\%$ overhead of the shuffle read in a reduce task (Figure \ref{fig:reducetask}). 
In addition, the heuristic algorithm can achieve a balanced pre-scheduling result, thus providing ~$80\%$ improvement in reduce stage completion time (Figure \ref{fig:reducestage}).

@@

% \subsubsection{Terasort}
% We also evaluate Terasort\footnote{http://sortbenchmark.org/YahooHadoop.pdf} --- a recognized shuffle intensive benchmark for distributed system analysis. 
% Terasort consists of two consecutive shuffles. 
% The first shuffle reads the input data and uses a hash partition function for re-partitioning. 
% As shown in Figure \ref{fig:terasort}, Spark with SCache runs 2 $\times$ faster during the reduce stage of the first shuffle, which is consistent with the results in Section \ref{simpledag}. 
% It further proves the effectiveness of SCache's optimization.

% The second shuffle of Terasort partitions the data through a Spark RangePartitioner. 
% % As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task. So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.
% In the second shuffle, almost $93\%$ of input data of a reduce task is produced by one particular map task. 
% So we take the second shuffle as an extreme case to evaluate the heuristic locality swap of SCache.
% In this shuffle, Spark schedules a reduce task to the node that produces most input data. 
% By doing this, Spark minimizes the shuffle data through network. 
% At the same time, Figure \ref{fig:terashuffle} reveals that SCache produces exactly same network traffic as Spark. 
% It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load. 
\begin{figure*}
	\centering
	\includegraphics[width=.8\textwidth]{fig/tpcds}
	\caption{TPC-DS Benchmark Evaluation}
	\label{fig:tpcds}
	\vspace{-1em}
\end{figure*}

\subsubsection{Industrial Production Workload}
% We also evaluate some queries from TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
% TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.). 
% TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. 
TPC-DS\footnote{http://www.tpc.org/tpcds/} contains 99 queries and is considered as a standardized industry benchmark for testing big data systems. 
% We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute. 
As shown in Figure \ref{fig:tpcds}, the horizontal axis is query name and the vertical axis is query completion time. 
Note that we skip some queries due to the compatible issues. 
Spark with SCache outperforms the original Spark in almost all tested queries. 
Furthermore, in some shuffle-heavy queries, Spark with SCache outperforms original Spark by an order of magnitude. 
% It is because that those queries contain shuffle-heavy operations such as \textit{groupby}, \textit{union}, etc.
The overall reduction portion of query time that SCache achieved is $40\%$ on average. 
Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.

\begin{figure}
	\centering
	\begin{subfigure}{.8\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_terasort_scache}
		\caption{\color{black}Hadoop MapReduce with SCache}
		\label{fig:hadoop_terasort_scache}
	\end{subfigure}
	\begin{subfigure}{.8\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_terasort_origin}
		\caption{\color{black}Hadoop MapReduce without SCache}
		\label{fig:hadoop_terasort_origin}
	\end{subfigure}
	\caption{\color{black}CPU utilization and I/O throughput of a node during a Hadoop MapReduce Terasort job}
	\label{fig:hadoop_terasort}
\end{figure}

{\color{black}
\subsection{Hadoop MapReduce with SCache}

@@

% Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort. Both figures have the same proportion of time. 
% As Figure \ref{fig:hadoop_terasort} shows, Hadoop MapReduce with SCache brings $15\%$ of total time optimization with 384GB input data size. 
As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase and the shuffle phase and the reduce phase start simultaneously. The beginning part of reduce phase needs to wait for network transfer because a large amount of shuffle data reaches the network bottleneck. This causes the CPU resources to be idle. 
On the other hand, in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache starts pre-fetching in the map phase. This avoids the reduce phase waiting for the shuffle data. Furthermore, pre-fetching utilizes the idle I/O throughput in the map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after decoupling shuffle, Hadoop MapReduce with SCache optimizes Terasort overall completion time by up to $15\%$ and an average of $13\%$ with input data sizes from 128GB to 512GB.
}

% \subsection{Overhead of Sampling}
% We evaluate the overhead of sampling with different input sizes and numbers of nodes. 
% In Figure \ref{fig:sampling}, the overhead of sampling only grows with the increase of input size on each node, but remains relatively stable when the cluster size scales up.
% Since the shuffle data is short-lived, write-once, and read-once, the central controller of SCache does not have to collect and manage complex metadata. 
% Meanwhile, most of the optimizations such as fetching and storing shuffle data are finished by workers independently. 
% So the cost of pre-scheduling algorithm and memory management are unlikely to make the master become the bottleneck of the scalability.
% Combined with the sampling overhead evaluation, we believe that SCache is scalable.

\begin{figure}
    \centering
    \begin{minipage}{0.4\textwidth}
        \centering
        \includegraphics[width=.8\linewidth]{fig/hadoop_terasort_time} % first figure itself
        \caption{\color{black}Hadoop MapReduce Terasort Completion Time}
		\label{fig:hadoop_terasort_time}
    \end{minipage}\hfill
    % \begin{minipage}{0.4\textwidth}
    %     \centering
    %     \includegraphics[width=.8\linewidth]{fig/sampling} % second figure itself
    %     \caption{Sampling Overhead}
	% 	\label{fig:sampling}
    % \end{minipage}
\end{figure}
